taxize: taxonomic search and retrieval in R

### 2013-10-04 f1000_rev/taxize_ms.Rnw
added a few changes to the main ms, #178

\section*{Introduction}
Evolution by natural selection has led to a hierarchical relationship among all living organisms.  Thus, species are categorized using a taxonomic hierarchy, starting with the binomial species name (e.g, \emph{Homo sapiens}), moving up to genus (\emph{Homo}), then family (\emph{Hominidae}), and on up to Domain (\emph{Eukarya}). Biologists, whether studying organisms at the cell, organismal, or community level, can put their study objects into taxonomic context, allowing them to know close and distant relatives, find relevant literature, and more.

@@

The R language is widely used by biologists, and now has over 5,000 packages on the Comprehensive R Archive Network (CRAN) to extend R. R is great for manipulating, visualizing and fitting statistical models to data. Gentleman et al. \cite{gentleman_bioconductor:_2004} give a detailed discussion of advantages of R in computational biology. Getting data from the web will be increasingly common as more and more data gets moved to the cloud. Therefore there is a need to get data from the web directly into R. Increasingly, data is available from the web via application programming interfaces (API). These allow computers to talk to one another using code that is not human readable, but is machine readable. Web APIs often define a number of methods that allow users to search for a species name, or retrieve the synonyms for a species name, for example. A further advantage of APIs is that they are language agnostic, meaning that data can be consumed in almost any computing context, allowing users to interact with the web API without having to know the details of the code. Moreover data can be accessed from every computer, whereas for example an Excel file can only be opened in a few programs.

@@

One available data source in taxize is The Plant List \url{http://www.theplantlist.org}. The connection in taxize is done via the \emph{taxonstand} package \cite{Cayuela_2012,taxonstand} that solely interacts with the Plant List. We provide a few convenience functions that wrap \emph{taxonstand} into taxize.

>>>>

\section*{Introduction}
Evolution by natural selection has led to a hierarchical relationship among all living organisms.  Thus, species are categorized using a taxonomic hierarchy, starting with the binomial species name (e.g, \emph{Homo sapiens}), moving up to genus (\emph{Homo}), then family (\emph{Hominidae}), and on up to Domain (\emph{Eukarya}). Although taxonomic classifications are human constructs created to understand the real phylogeny of life \cite{benton2000}, they are nonetheless essential to organize the vast diversity of organisms. Biologists, whether studying organisms at the cell, organismal, or community level, can put their study objects into taxonomic context, allowing them to infer close and distant relatives, find relevant literature, and more.

@@

The R language is widely used by biologists, and now has over 5,000 packages on the Comprehensive R Archive Network (CRAN) to extend R. R is great for manipulating, visualizing and fitting statistical models to data. Gentleman et al. \cite{gentleman_bioconductor:_2004} give a detailed discussion of advantages of R in computational biology. Getting data from the web will be increasingly common as more and more data gets moved to the cloud. Therefore, there is a need to get data from the web directly into R. Increasingly, data is available from the web via application programming interfaces (API). These allow computers to talk to one another using code that is not human readable, but is machine readable. Web APIs often define a number of methods that allow users to search for a species name, or retrieve the synonyms for a species name, for example. A further advantage of APIs is that they are language agnostic, meaning that data can be consumed in almost any computing context, allowing users to interact with the web API without having to know the details of the code. Moreover data can be accessed from every computer, whereas for example an Excel file can only be opened in a few programs.

@@
